TODO

### 2021-03-30 paper2/paper.tex
Add acknowledgements for SC and CS
Add preliminary discussion of DY
Change title

\usepackage[UKenglish]{babel}
%\usepackage{booktabs}
%\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
%\usepackage{listings}
\usepackage{lmodern}
%\usepackage[binary-units=true,detect-weight=true,group-digits=false,table-format=4.2]{siunitx}
%\usepackage{xcolor}
%\usepackage[percent]{overpic}
%\usepackage{mathcomp}
%\usepackage{tabularx}
%\usepackage{textcomp}

@@

\title{PineAPPL: combining EW and QCD corrections\\
  for fast evaluation of LHC processes}

@@

%\arxivnumber{}

@@

\input{sec-introduction}
\input{sec-results}
\input{sec-conclusion}

@@

\acknowledgments
TODO

>>>>

\usepackage[UKenglish]{babel}
%\usepackage{booktabs}
%\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
%\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true,group-digits=false,table-format=4.2]{siunitx}
%\usepackage{xcolor}
%\usepackage[percent]{overpic}
%\usepackage{mathcomp}
%\usepackage{tabularx}
%\usepackage{textcomp}

@@

\title{TODO}

@@

\arxivnumber{TODO}

@@

\input{sec-introduction}
\input{sec-results}
\input{sec-datasets}
\input{sec-conclusion}

@@

\acknowledgments
S.C.\ and C.S.\ are supported by the European Research Council under the European Union's Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).

\input{app-misc}
